\chapter{Chapter 3: Races}
\section{Half-Gombrut}
\begin{quotebox}
As Grar realized, that not everybody was thinking good about his heriatage, he ran. Even tho, he was  stronger than any human, he was nowhere accepted into any kind of  society. He fought in a 100 Battles and killed more than any human, but his heriatage was his doom. Not as smart as he was, he walked straigth into a trap, build by 2 mortal enemys: A Gombrut and a Human
\end{quotebox}

\subsection{Left Behind}
Half-Gombruts' look like Humans, in a gray-isch skin. They have strong, well defined muscels and are more tall than wide. They apear as if a Human was streched out to far. Most of them are around 7 feet tall, yet none of these is smaller  than $6^{1/2}$ feet. Yet, because of the weigh only around 175 - 215 pounds. Because they are related to the Gombrut, the oldes Half-Gombruts are around 1000 years old and mature at around 100 years. The older a Half-Gombrut becomes, the more it is overdrawn with Stone, as if the creature becomes one with the mountain.

They originaly derive from Humans, yet they are way less intelligent than humans. Some going so far, as being as stupid as a simple bug. Theire clumsyness is infamous. They almost always fail at basic task, such as grabing berrys from a small tree in a spectacular fasion. Most of the time, the only trouble they have, is the trouble they get themself into, if they are to clumsy to correctly performe any task.

Even though they are ousiders in nearly any society, they are verry kind and good creatures, healping anyone in need.

\newpage

\subsection{Antisocial Genes}
Because neither the Humans nor the Gombruts are willing to accept a Half-Gombrut into theire society, Half-Gombruts are antisocial loners in theire nature. Some form small tribes and some integrate themself into smaller groups, but most of them are always on theire own at adventures or living in caves, naturaly acouring in mountains.

They are friendly towards all creatures, yet they know to defend themself. They inherited this trait from theire Gombrut ancestors. Half-Gombruts thrief towards building up theire own perfect world, just like theire Human ancestors. They hold true to most of the prejudice against Humans and against Gombruts. 

\begin{commentbox}{Uncommon Races}
The Half-Gombrut and every other Race in this Chapter are uncommon. They don't exist in every world of D\&D and are less widespread than other races.\\
\textbf{Half-Gombrut.} Half-Gombruts are verry rare and scattered over nearly all continents. They are so rare because most of them are never leaving there home-mountain.\\
\textbf{Half-Weylins.} Half-Weylins tend to live in forrests and socialice as little as possible, which is why they are almost never seen in many cities.\\
\end{commentbox}

\subsection{Half-Gombrut Names}
Half-Gombruts earn theire name from theire parents, when they are born. This name consists 2 parts. A name, and a family name. More often than not, Half-Gombruts have two family names, because theire parents had two different. Once they mature, most Half-Gombruts tend to give themself a new name, while keeping theire family name(s).

\begin{paperbox}{The names of Half-Gombruts}
Half-Gombruts are proud of there names, often reffering to the name as "the most beautiful thing in the world", even tho it sounds more like a stone rolling at an uneven surface. As you choose you name, keep that in mind.
\end{paperbox}

\textbf{Male Names:}
Dombra, Grutro, Ernero, Meratro, Utragro, Pretegre, Kumanrare
\textbf{Female Names:}
Arear, Zurare, Undradar, Kirantar, Hubrate, Gultar, Lurare
\textbf{Family Names:}
Stoneeater, Rockseeker, Meatservant, Goldfinder, Crowholder, Mountainclaimer, Dirtgrower

\subsection{Half-Gombrut Traits}
Your heritage manifests in different forms.

\textbf{Ability Score Increase.} Your Constitution score increases by 2, and your Strength score increases by 2. Your Intelligence decreases by 1.

\textbf{Age.} Your Half-Gombrut ages slowly. They atain the development off a 10-year-old Human by the age of 60 and reach adulthot by 100. They live to be up to 1000 Years.

\textbf{Alignmennt.} Half-Gombruts tend towards a Good alignment, verry rarely if ever dipping into the Chaotic or even Evil alignment. Yet they are not bound to rules of any kind, except they put on themselfs. Most Half-Gombruts lean towards a Neutral or Chaotic alignment.

\textbf{Size.} Half-Gombruts are tall and slim creatures, even tho they are verry muscular. They are around 7 - $7^{1/4}$ feet tall, but never fall beneth $6^{1/2}$ feet.

\textbf{Speed.} Your base walking speed is 25 feet.

\textbf{Hardened Skin.} Because of your age and your diet, you have "stone in your blood". Your skin is verry thick and not as easy penetrable as most other skin. Your base AC is 12 instead of 10.

\textbf{Damage Resistance.} You have resistance to slashing damage.

\textbf{Fight Focus.} A Half-Gombrut can concentrate so hard, that the stone on his body changes the position. Your armor-class increases by 2 (after calculation). Once you used this trait, you can't use it again until you finish a long rest.

\textbf{Languages.} You can speak, read and write Common and Gombrut. Common though is a bit stuttering. You don't socialize much, so you can't practice this languages and with your parents you mostly speak Gombrut. So you are switching, leaving out words and changing the basic structure of some sentences.

\textbf{Darvision} Because you live in pitch black environments most of the time, you have superior vision in dim and dark conditions. \darkvision{60}

\begin{commentbox}{Playing an Half-Gombrut}
Half-Gombruts would act clumsy or awkward in most situations of social interactions without realising it. They never learned it, so they don't know it better. But mostly they don't care, so they never will learn it anyways.
\end{commentbox}

\newpage
\section{Half-Weylin}

\begin{quotebox}
Kraa reached the east point of the forwarr, he stumbled upon some remains of the fight, that had just ended. Kraa was sick of this all. He wanted to get away fom his old life. After nearly 4 Weeks in on the run, Kraa encountered a Human. Happy and full of hope he asked for a helping hand to get out of this nightmare, but only found the tip of a long sword, piercing his instesticals. "Why?", was the last word out of his mouth.
\end{quotebox}

\subsection{Wild Anatomy}
Half-Weylins are looking like a verry harrie hair, with a twist. They appear wolf-like in many forms and most of the time, they could  be mistaken for one. Other than Werewolfs tho, theire faces and Hands appear Human like. The hip of an Half-Weylin is formed in a way, that the Half-Weylin can walk on 2 feet just as good as on his feet and hand combined, like a wolf.

They come in at around $4^{3/4}$ - $5^{1/2}$ feet, a bit smaler than the average Human and a bit bigger than the average Weylin. They have a weird inner antonomy, which is not as reliably and consistantly working as a Humans. Most of them grow up to become 60 years old. Because they live in the woods and have to grow up quickly, they mature at around 1 - 2 years and start hunting prey. At around 8 years, nearly all Half-Weylins have learned to walk only on there 2 feet, but they take around 2 more years to get used to it.

Tho there heritage is both Human and Weylin, they tend to deny there Weylin heritage and adopting Human-history. Even there inteligence contests that, of the average Human. Thats why most of them lean twoards inflicting non-physical damage. But do not underistimate the strength, they can bring up, if needed. Even tho they akt within the boundries of what is considered to be "good", they are not likedd by humans because of there Weylin heritage.

\subsection{Pack-Live}
Half-Weylins which live in the east of sobra or on a nother continent all together tend to live the life of a loner, feeding on prey that they encounter on a dayli bases. But those, who have the luck to live with there own, do so. They form small Packs, which consists 1 alpha and every other Half-Weylin beneth him. Tho he is the alpha, Half-Weylins tend to have some sort of democracy in order.

Some of them live in houses, whilest others tend to sleep outside in the wilderness. This is nothing more than a taste realy, depending on the individual Half-Weylin. Most of these Half-Weylins believe nothing in terms of gods, but if they follow a god, they do it with great passion.

\begin{paperbox}{The Curse of Ancestory}
Most Humans dont like Weylins, but some hate any form of Weylin to the depths of there heart. Expect to get some rude comments along the way of the adventure or, in the worst case, even random attacks from Humans.\\
That includes: 
\begin{itemize}
\item Humans, that served in an army fighting against the Weylins.
\item Humans, that lost somebody important to them in a fight against Weylins.
\item Other creatures, that where affected by the war between Humans and Weylins.
\end{itemize}
Your character knows that and would most likely acts humble in such situations, to strengthen the good reputation of Half-Weylins. Except if your Character does not care about that or is marked by the daily hate against him.
\end{paperbox}
\subsection{Half-Weylin Names}
A typical Half-Weylin names constist of a name, given at birth and the pack he grew up in.\\

\textbf{Male Names:}\\
TODO\\
\textbf{Female Name:}\\
TODO\\
\textbf{Pack Names:}\\
TODO\\

\subsection{Half-Weylin Traits}
Your heritage manifests in different forms.

\textbf{Ability Score Increase.} Your Wisdom score increases by 2 and your Intelligence score increases by 1.

\textbf{Age.} Half-Weylins age verry fast. They live to be 60 years old and maturing at around 1 year.

\textbf{Alignmennt.} Half-Weylins tend to start with a neutral alignment, changing to evil as they age and observe the hostile and evil world around them. Half-Weylins living in a pack adopt the lawfull alignmennt and loners mostly adopt the chaotic alignment.

\textbf{Size.} Half-Weylins anatomy resemble partly that of a wolf. There size lies between $4^{3/4}$ - $5^{1/2}$, but mostly in the middle of this range.

\textbf{Speed.} Your base walking speed on foot is 20 feet and 40 on all fours.

\textbf{Versatile Walker.} As an action, you can choose to change the way you walk to \textit{"on two foot"} or \textit{"on all fours"}. However, you can't hold anything in your hands while on all fours. Wearing armor is okay, as long as it does not hinder the walking on all fours.

\textbf{Keen Senses.} You have proficiency in Perception check. In addition, you have advantage on perception checks that rely on smell or hearing.

\textbf{Claws.} Your claws are natural weapons, which you can use to make unarmed strikes. If you hit with them, you deal slashing damage equal to 1d4 + your Strength modifier, instead of bludgoning damage normal for an unarmed strike.

\textbf{Primal Instinkts} A Half-Weylin, thats currents hitpoints is beneth half his maximum hitpoints (rounded up) can use this trait to take an reaktion, whenever he takes damage. He can choose to walk 5 feet, in the direction of the source of the damage. After you heald above half the maximum hitpoints (rounded up), you have to take a long rest, bevore you can use this feature again.

\textbf{Darvision.} Because you live in a forrest, you have better sight in the dark than normal. \darkvision{30}

\textbf{Languages.} You can speak, read and write Common, Weylin and one language of your choice.

\begin{commentbox}{Playing an Half-Weylin}
Half-Weylins know about natures law and tend to leave other creatures as they are. Conflicts are nothing realy new to them, but they mostly keep out of the way of trouble relating to there Weylin ancestory. If your character is harrased, because he has a Weylin heritage, he would most likly not engage further into this debate.
\end{commentbox}


